%-------------------------
% Yash Gupta - Academic CV
% AI Researcher | Agentic Systems & AI Orchestration
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\titleformat{\section}{
  \large\bfseries
}{}{0em}{}[\titlerule]

% Custom commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubItem}[2]{
  \item
  \textbf{#1} \\
  {\small #2}
}

\begin{document}

%-------------------- HEADING --------------------

\begin{center}
    {\Huge \textbf{Yash Gupta}} \\ \vspace{4pt}
    {\normalsize AI Researcher \textbar{} Agentic Systems \& AI Orchestration} \\ \vspace{4pt}
    Delhi, India \\
    \faEnvelope \; \href{mailto:research.yashgupta@gmail.com}{research.yashgupta@gmail.com} \quad
    \faGithub \; \href{https://github.com/mryashdev}{github.com/mryashdev} \quad
    \faGlobe \; \href{https://mryashdev.in}{mryashdev.in} \quad
    \faGraduationCap \; \href{https://scholar.google.com/citations?hl=en&user=3uROiJIAAAAJ}{Google Scholar}
\end{center}

%-------------------- RESEARCH INTERESTS --------------------

\section{Research Interests}
Reliability and failure mode analysis of agentic AI systems, multi-agent orchestration architectures and task decomposition, trustworthy autonomous decision-making under ambiguous inputs, tool-augmented language models and agentic memory systems, evaluation frameworks for multi-step AI task completion.

%-------------------- EDUCATION --------------------

\section{Education}
\resumeSubHeadingListStart

\resumeSubItem
{B.Tech in Computer Science and Engineering (Lateral Entry)}
{Institute of Information Technology and Management (IITM), Janakpuri Campus, Delhi \hfill 2025 -- 2028 (Expected) \\
Currently pursuing BTech CS with research focus on agentic AI systems, multi-agent orchestration, and reliable autonomous decision-making pipelines.}

\vspace{4pt}

\resumeSubItem
{Diploma in Computer Engineering}
{Delhi Skill and Entrepreneurship University (DSEU), Rajokri Campus, Delhi \hfill 2022 -- 2025 \\
Foundation in systems programming, operating systems, and computer architecture.}

\resumeSubHeadingListEnd

%-------------------- RESEARCH EXPERIENCE --------------------

\section{Research Experience}
\resumeSubHeadingListStart

\resumeSubItem
{Independent Researcher --- Research \& Development \hfill 2024 -- Present \\\small\textit{Research initiated during final year of Diploma, continued through BTech.}}
{
\begin{itemize}[leftmargin=0.15in, topsep=0pt, itemsep=2pt]
  \item Building an evaluation framework to systematically test how agentic AI pipelines fail under ambiguous and adversarially crafted instructions.
  \item Developing a multi-agent task delegation system with context consistency tracking and partial failure recovery mechanisms.
  \item Studying task decomposition patterns in LangChain and LangGraph-based agents to identify failure modes in multi-step execution.
  \item Professional ML data annotation --- evaluating agentic AI outputs for instruction-following accuracy, reasoning consistency, and multi-step task completion quality.
\end{itemize}
}

\resumeSubHeadingListEnd

%-------------------- PUBLICATIONS --------------------

\section{Publications}
\resumeSubHeadingListStart

\resumeSubItem
{Failure Mode Taxonomy of Agentic AI Pipelines Under Ambiguous Instruction Sets}
{Yash Gupta. \textit{Research in progress. Manuscript planned. Target: NeurIPS 2027 Workshop on Agentic AI Systems.}}

\vspace{4pt}

\resumeSubItem
{Reliable Task Delegation in Multi-Agent Systems: Context Consistency and Partial Failure Recovery}
{Yash Gupta. \textit{Research in progress. Manuscript planned. Target: IEEE/ACM conference submission, 2027.}}

\resumeSubHeadingListEnd

%-------------------- RESEARCH PROJECTS --------------------

\section{Research Projects}
\resumeSubHeadingListStart

\resumeSubItem
{AgentStress --- Agentic Pipeline Failure Testing Framework \hfill In Development}
{Building a Python testing framework that sends crafted instruction variants to LangChain and LangGraph agents, logs tool-call sequences, and classifies failures into categories: instruction drift, premature termination, and tool-call hallucination. \\
\textit{Stack: Python, LangChain, LangGraph, OpenAI API}}

\vspace{6pt}

\resumeSubItem
{OrchestBot --- Multi-Agent Task Delegation System \hfill In Development}
{Building a lightweight orchestration layer where a planner agent breaks down user goals into an execution graph, dispatches subtasks to tool-specific agents (search, code, summarize), and merges outputs with conflict detection. \\
\textit{Stack: Python, LangGraph, OpenAI API, Redis}}

\resumeSubHeadingListEnd

%-------------------- TECHNICAL SKILLS --------------------

\section{Technical Skills}
\begin{description}[font=$\bullet$]
\item {AI \& ML: PyTorch, LangChain, LangGraph, OpenAI API, Prompt Engineering, ML Evaluation}
\vspace{-4pt}
\item {Agentic Systems: Agentic Pipelines, Multi-Agent Orchestration, RAG Architecture, Vector Databases}
\vspace{-4pt}
\item {Programming: Python, SQL, REST APIs}
\vspace{-4pt}
\item {Tools \& Infrastructure: Git, Linux, Redis, Data Annotation Pipelines}
\end{description}

%-------------------- ACADEMIC INITIATIVES --------------------

\section{Academic Initiatives}
\resumeSubHeadingListStart

\resumeSubItem
{Graduate School Preparation --- UTokyo 2028}
{Targeting MEXT University Recommendation track at University of Tokyo (Graduate School of Information Science and Technology, IST). Building research profile through manuscript preparation, experiment documentation, and targeted professor outreach.}

\vspace{4pt}

\resumeSubItem
{Japanese Language --- JLPT N4 Certified, Targeting N3}
{Certified at JLPT N4. Active Japanese language study as part of long-term research integration strategy for collaboration with Japanese research groups.}

\resumeSubHeadingListEnd

%-------------------- LANGUAGES --------------------

\section{Languages}
\begin{description}[font=$\bullet$]
\item {English: Fluent}
\vspace{-4pt}
\item {Japanese: JLPT N4 Certified (targeting N3)}
\end{description}

%-------------------- REFERENCES --------------------

\section{References}
Available upon request.

\end{document}
